---
title: "HW6"
author: "Wenyi"
date: "12/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(mgcv)
```


##problem 1
```{r data wrangling}
bw_df=
  read_csv(file = "./data/birthweight.csv")%>%
  janitor::clean_names()%>%
  mutate(
    babysex = recode(babysex, `1` = "male", `2` = "female"),
    babysex = factor(babysex),
    frace=recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    frace = factor(frace),
    malform = recode(malform, `0` = "absent", `1` = "present"),
    malform = factor(malform),
    mrace = recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"),
    mrace = factor(mrace)) 
  
```

#mdoel fitting
```{r}
fit= lm(bwt ~ blength+ babysex + delwt+ mheight+ppwt+ppbmi, data = bw_df)

summary(fit)
summary(fit)$coef
coef(fit)

fit %>% 
  broom::glance()

bw_df %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = blength, y = resid)) + geom_violin()
```
The model fitting process includes the hypothesized structure for the factors that underly birthweight. The guess is that the mother's weight, height and any other related (like BMI) will be associated with baby's birthweight. After guessing, check the p-value of t-test for each potential coefficient and keep the meaningful variable in the model.


#model 1
```{r comparing model 1}
fit1= lm(bwt ~ blength + gaweeks, data = bw_df)

summary(fit1)
summary(fit1)$coef
coef(fit1)

fit1 %>% 
  broom::glance()
```

#model 2
```{r comparing model 2}
fit2 = lm(bwt ~ bhead + blength + babysex +bhead*blength+bhead*babysex+babysex*blength+bhead*babysex*blength, data = bw_df)

summary(fit2)
summary(fit2)$coef
coef(fit2)

fit2 %>% 
  broom::glance()
```

# Comapring model 
```{r model comparing}
fit= lm(bwt ~ blength+babysex + delwt+ mheight+ppwt+ppbmi, data = bw_df)
fit1= lm(bwt ~ blength + gaweeks, data = bw_df)
fit2 = lm(bwt ~ bhead + blength + babysex +bhead*blength+bhead*babysex+babysex*blength+bhead*babysex*blength, data = bw_df)

bw_df %>% 
  gather_predictions(fit, fit1, fit2) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = blength, y = bwt)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)

cv_df =
  crossv_mc(bw_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

```
Conclusion:
The fit2 model is the better model


##Problem2
```{r data warngling}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r make a plot}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

weather_df %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

```{r bootstrap}
bootstrap_df = 
  weather_df %>% 
  sample_frac(size = 5000, replace = TRUE) %>% 
  arrange(tmin)

lm(tmax~tmin, data = bootstrap_df)
```

```{r function}
boot_df = function(df) {
  
  sample_frac(df, size = 5000, replace = TRUE)
  
}
```

```{r tracking}
boot_strap_df = 
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_df(weather_df))
  )
```

